Reviews & Posts:

1. @FitnessFanaticKate (Twitter): Obsessed with the new Cymbal Direct leggings! The fabric is so soft and supportive. Finally, a legging that doesn't slip during my runs! #CymbalDirect #Activewear #LeggingsLove

2. Amazon Review (5 Stars): "Bought the 'Pulse' running shorts. Lightweight, breathable, and dries quickly. Exactly what I needed for summer workouts!"

3. @GymRatGary (Instagram): Cymbal Direct's new line is…okay. Nothing groundbreaking, but the 'Endure' t-shirt is decent quality for the price. #CymbalDirect #GymLife #FitnessApparel

4. Facebook Post (Sarah Miller): "Anyone else try the new Cymbal Direct stuff? I got the 'Flow' yoga pants, and they're a little too tight around the waistband, even though I ordered my usual size. Disappointed. 😕"

5. CymbalDirect.com Review (4 Stars): "The 'Stride' tank top is great for layering. I love the color options. Only downside is the material wrinkles easily."

6. @SweatyBetty123 (Twitter): Cymbal Direct's marketing is on point, but the actual apparel? Meh. Expected more from the hype. #CymbalDirect #Overrated #FitnessFail

7. Amazon Review (1 Star): "Seam ripped after only two washes. The 'Power' hoodie is NOT durable. Waste of money! Returning it."

8. @RunnergirlRachel (Instagram Story): New Cymbal Direct sports bra! Testing it out on today's long run. Fingers crossed for good support! #CymbalDirect #SportsBra #Running

9. Facebook Post (John Davis): "Just received my Cymbal Direct order. The packaging was nice, but the 'Apex' training shorts feel a bit…cheap? Will see how they hold up."

10. CymbalDirect.com Review (5 Stars): "Absolutely love the 'Zenith' jacket! Perfect for chilly morning runs. Lightweight, windproof, and looks great!"

11. @YogaWithMia (Twitter): The Cymbal Direct 'Balance' leggings are so comfy for my yoga practice! They stay in place and feel like a second skin. Highly recommend! #CymbalDirect #Yoga #Activewear

12. Amazon Review (3 Stars): "The color of the 'Velocity' shirt is different in person than it appeared online. The fit is okay, but I wouldn't buy it again."

13. @CrossfitChris (Instagram): Just crushed a WOD in my new Cymbal Direct 'Strength' shorts! Good range of motion, but they could be a little tougher. #CymbalDirect #Crossfit #Fitness

14. Facebook Post (Lisa Garcia): "Does anyone know if Cymbal Direct runs true to size? I'm hesitant to order online. Thanks!"

15. CymbalDirect.com Review (2 Stars): "The sizing chart is completely off. Ordered a medium based on my measurements, and it's way too small. Annoying!"

16. @HikingHannah (Twitter): Exploring the trails in my Cymbal Direct 'Summit' hiking pants! They're water-resistant and comfortable. #CymbalDirect #Hiking #OutdoorAdventures

17. Amazon Review (4 Stars): "Good value for the price. The 'Energy' tank is cute and functional for everyday wear."

18. @PilatesPete (Instagram): Trying out the new Cymbal Direct 'Control' top during my Pilates session. Feels supportive but a little restrictive. #CymbalDirect #Pilates #ActivewearReview

19. Facebook Post (David Lee): "Cymbal Direct customer service is terrible. Trying to return an item, and they're not responding to my emails."

20. CymbalDirect.com Review (5 Stars): "Finally, a brand that understands the needs of plus-size athletes! The 'Empower' collection is amazing. Comfortable, supportive, and flattering. Thank you, Cymbal Direct!"